---
title: "Reproduced Analysis"
author: "Gathoni"
date: "2026-01-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This project is a reproduction of analysis from Hackenberg et al., *Levers of Political Persuasion with Conversational AI* (2025). Specifically, my aim in this project was to reproduce their analysis on the effect of personalisation on persuasion.

## Overview of Findings

When I reran the analysis on the effect of personalisation on persuasion, I found the same results as the initial study: while there was a statistically significant effect, the mean difference was less than a point (0.65).
```{r load_data, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
# Load packages
library(dplyr)
library(ggplot2)
library(lmtest)

# Load data
my_data_clean <- readRDS("my_data_clean.rds")

# Check current structure
cat("Current personalize variable:\n")
print(table(my_data_clean$personalize))

# Convert to numeric: generic = 0, personalized = 1
my_data_clean$personalize_numeric <- ifelse(my_data_clean$personalize == "personalized", 1, 0)
cat("\nConverted to numeric:\n")
cat("0 = generic, 1 = personalized\n\n")


```
```{r}
# Pearson correlation
cor_test <- cor.test(my_data_clean$personalize_numeric, 
                     my_data_clean$post_minus_pre, 
                     method = "pearson")
cor_test 
```
```{r}
# Interpretation 
if(cor_test$p.value < 0.05) {
  cat("✓ Significant correlation (p < 0.05)\n")
  if(cor_test$estimate > 0) {
    cat("  → Positive correlation: Personalization associated with higher persuasion shift\n")
  } else {
    cat("  → Negative correlation: Personalization associated with lower persuasion shift\n")
  }
} else {
  cat("✗ No significant correlation (p ≥ 0.05)\n")
  cat("  → No linear relationship between personalization and persuasion shift\n")
}
```
```{r}
# Descriptive statistic by group
generic_data <- my_data_clean[!is.na(my_data_clean$personalize) & 
                                !is.na(my_data_clean$post_minus_pre) &
                                my_data_clean$personalize == "generic", ]
personalized_data <- my_data_clean[!is.na(my_data_clean$personalize) & 
                                     !is.na(my_data_clean$post_minus_pre) &
                                     my_data_clean$personalize == "personalized", ]
# Difference between the groups
mean_diff <- mean(personalized_data$post_minus_pre, na.rm = TRUE) - 
  mean(generic_data$post_minus_pre, na.rm = TRUE)
cat("  Mean difference:", round(mean_diff, 2), "points\n")
cat("  Personalized", ifelse(mean_diff > 0, "HIGHER", "LOWER"), "than generic\n")

```
```{r}
# Boxplot
ggplot(my_data_clean, aes(x = personalize, y = post_minus_pre, fill = personalize)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(alpha = 0.1, width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, 
               fill = "red", color = "darkred") +
  labs(
    title = "Persuasion Shift by Message Type",
    subtitle = paste0("Pearson r = ", round(cor_test$estimate, 3), 
                     ", p = ", format.pval(cor_test$p.value, digits = 3)),
    x = "Message Type",
    y = "Persuasion Shift (Post - Pre)",
    caption = "Red diamond = mean"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  ) +
  scale_fill_manual(values = c("generic" = "#E41A1C", "personalized" = "#377EB8"))
```
## Conclusion

The reproduced findings confirm the initial results from Hackenberg et al. (2025). While personalisation showed a statistically significant effect on persuasion, the practical significance remains limited with a mean difference of 0.65 points between conditions.
